---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hebr

<!-- badges: start -->
<!-- badges: end -->

The goal of hebr is to help useRs handle Hebrew text within R code and output.

## Installation

You can install the development version of hebr from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("matanhakim/hebr")
```

## Example

This is a basic example of fixing an RTL issue when writing in Hebrew:

```{r example}
library(hebr)
x <- "סימני ניקוד בסוף המשפט."
str_heb(x)
```

You can also use it in plots, for example:

```{r plot_1, echo = FALSE}
library(ggplot2)
ggplot(mtcars, aes(cyl)) +
  geom_bar() +
  xlab("צילינדרים!")
```

Notice how the exclamation mark is on the right-hand side, but it should be on the left.
use `str_heb()` to solve it, like this:

```{r plot_2, echo = FALSE}
ggplot(mtcars, aes(cyl)) +
  geom_bar() +
  xlab(str_heb("צילינדרים!"))
```

Now the exclamation mark is on the left-hand side, like it should.
